---
title: "Assignment 1 v2"
author: "Gabrielle Carpenito"
date: "2025-09-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

```
> mydata <- (Typical_Employee_Survey_Data)
> summary(mydata$age)
Length  Class   Mode 
     0   NULL   NULL 

> summary(mydata$gender)
Length  Class   Mode 
     0   NULL   NULL 

> 
> summary(mydata$JobSatisfaction)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   1.000   1.000   1.631   2.000   4.000 

> summary(mydata$ImpJobCharacteristic)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   2.000   5.000   3.705   5.000   5.000 

> summary(mydata$ImpJobCharacteristic)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   2.000   5.000   3.705   5.000   5.000 

> summary(mydata$YearsEmployer)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  0.080   2.000   5.000   8.224  11.000  52.250 

> summary(mydata$PromotionLikelihood)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   2.000   4.000   3.287   5.000   5.000 

> summary(mydata$DecisionAuthority)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   2.000   2.000   2.279   3.000   4.000 

> summary(mydata$BudgetDecision)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   1.000   1.000   1.451   2.000   2.000 

> summary(mydata$OrganizationPride)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   1.000   2.000   1.787   2.000   4.000 

> summary(mydata$JobChurnForPay)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   2.000   4.000   3.254   4.000   5.000 

> summary(mydata$WorkRelations)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   1.000   2.000   1.787   2.000   4.000 

> mydata$Gender <- factor(mydata$Gender)

> mydata$JobSatisfaction <- factor(mydata$JobSatisfaction)

> plot(mydata$DecisionAuthority,mydata$BudgetDecision)

> plot(mydata$JobSatisfaction,mydata$YearsEmployer)

> barplot(mydata$JobSatisfaction,mydata$YearsEmployer)


